Converging High-Throughput and High-Performance Computing: A Case Study

### 2017-04-04 abstract.tex
reduction in abstract.

The computing systems used by LHC experiments has historically consisted of
the federation of hundreds to thousands of distributed resources,  ranging in
scale from small to mid-size resource. As the LHC prepares for Run 3 in
$~\approx$ 2022 and the high-luminosity era (Run 4), it is anticipated that
the data volumes that will need analyzing will increase by factors of 10-100
compared to the current phase (Run 2). Data will be larger in volume but will
also require more sophisticated computational processing.  In spite of the
impressive scale of the existing distributed computing solutions, the
federation of small to mid-size resources will be insufficient to meet
projected supply. This paper is a case study of how the ATLAS experiment has
embraced leadership class high-performance computing in conjunction with
traditional distributed high-throughput computing. Specifically, we discuss
the experience of integrating PanDA WMS with the DOE leadership computing
facility (Titan) to reach sustained production scales of approximately 51M
core-hours a years. This state-of-practice paper provides three main
contributions:  (i) a critical evaluation of the many design and operational
considerations that have been taken to support the sustained, scalable and
production usage of Titan for historically high-throughput workloads; (ii) a
preliminary characterization of a next generation executor   for PanDA to
support non- traditional heterogeneous workloads and advanced execution modes;
and (iii) early lessons and guidance as the community looks forward to
designing the next generation of online analytical platforms, for how current
and future experimental and observational systems can be integrated with
production supercomputers in a general and extensible manner.

>>>>

% As the LHC prepares for Run 3 in
% $~\approx$ 2022 and the high-luminosity era (Run 4), it is anticipated that
% the data volumes that will need analyzing will increase by factors of 10-100
% compared to the current phase (Run 2). Data will be larger in volume but will
% also require more sophisticated computational processing.

The computing systems used by LHC experiments has historically consisted of
the federation of hundreds to thousands of distributed resources, ranging in
scale from small to mid-size resource.  In spite of the impressive scale of
the existing distributed computing solutions, the federation of small to mid-
size resources will be insufficient to meet projected demands of Run 3 (and
4). This paper is a case study of how the ATLAS experiment has embraced Titan
-- a DOE leadership facility in conjunction with traditional distributed high-
throughput computing to reach sustained production scales of approximately 51M
core-hours a years. The three main contributions of this paper are:  (i) a
critical evaluation of design and operational considerations  to support the
sustained, scalable and production usage of Titan;  (ii) a preliminary
characterization of a next generation executor for PanDA to support new
workloads and  advanced execution modes; and (iii) early lessons as  for how
current and future experimental and observational systems can be integrated
with production supercomputers and other platforms in a general and extensible
manner.
